---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Nepalwildlife

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/Nepalwildlife)](https://CRAN.R-project.org/package=Nepalwildlife)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

Nepalwildlife package brings together a list of wild animals and plants found in Nepal. It contains 1 tibble named `nepal_wildlife`.

## Installation

You can install the released version of Nepalwildlife from [Github](https://github.com/abhinabkadel/Nepalwildlife) with:

``` {r eval = FALSE}
install.packages("devtools")
devtools::install("abhinabkadel/Nepalwildlife")
```

## Example

How many species fall under different taxonomic groups in Nepal? Let's solve it using the dataset:

```{r example, message = FALSE}
library(Nepalwildlife) 
library(tidyverse)

nepal_wildlife %>% 
  count (`Taxonomic Group`)
```

## Steps used to Build the package:

### Initial setup:
 1. Load devtools using `library(devtools)`
 2. Use `create_package(pathname/Nepalwildlife)`. This created a folder named **Nepalwildlife** with skeleton for the package contents such as 
    DESCRIPTION and an R project file. 
 3. In the new Rstudio session that is opened, load usethis package using `library(usethis)`
 4. Set up git repo using use_git(). Perform initial commit and restart RStudio to activate the **Git** pane. 
 
### Place the dataset:
 1. Create a directory for raw data using `use_data_raw()`
 2. Add the dataset downloaded from the **Map of Life** in _.csv_ form into the newly created **data-raw** folder. 
 3. Add a R script titled `nepal_wildlife.R` in the folder, which converts the csv to a tibble in the .R file.
    - Include `usethis::use_data()` at the bottom of this R script to create a .rda data object in the **data** folder
 4. Check to __data__ folder in the root directory to see if *nepal_wildlife.rda* object exists. 
 
### Create documentation:
 1. Create a new R script called nepal_wildlife.R in the **R** folder in the root directory. 
 2. Create roxygen style documentation in it, ending with the line `"nepal_wildlife"`
    - There is not need to use `@export` tag because I am not creating any function and it was advised in class not to do so. 
 3. Run `document()`
 
### Tests for package:
 1. `use_testthat()` to create a **tests** folder in the root directory
 2. `use_test("nepal_wildlife")` creates an R file with my tests in it.
 3. Write test codes using `expect_` statements to check if:
    - the variable names of the dataset are as expected.
    - dataset is stored as a tibble
    - the the dataset has expected number of observations. 
 4. Check if tests pass using `test()`   
    
### Update DESCRIPTION file:
 1. Open DESCRIPTION file in a code editor
 2. Edit the **Title**, **Authors** and **Description** fields as necessary.
 3. Add license info using `usethis::use_mit_license("Abhinab Kadel")`
 4. Add dependencies using `use_package()`. The following packages are listed under the **@import** option:
    - Package tests specified above use _dplyr_ and _tibble_ packages. 
    - Vignette uses _stringr_ and _ggplot2_
    
### Add README and vignette:
 1. Create readme using `use_readme_rmd( )` and build it using `build_readme( )`. 
 2. Create vignette using `use_vignette("nepal_wildlife")` and build it using `build_vignette()`.
 
### Install package:
  Use `devtools::install()`
 
### Linking local repository to a remote repository
 1. Create a remote repository on Github called `Nepalwildlife`
 2. Push package contents from _local_ repo to _remote_ repo using the instructions provided in Github. 
 
### For optional tasks:
 1. Run `usethis::use_code_of_conduct()` to create a code of conduct text. Then, paste it to the README file (see below)
 2. Create a NEWS.md file using `use_news_md()`
 2. Run `usethis::use_version()` and select **minor** increment to set the package version to 0.1.0
      - This adds a new heading in the NEWS.md file with the package name and version nr. 
 3. Update information to the [NEWS.md](Nepalwildlife/NEWS.md) file. 
 4. Build the website:
      - Activate **pkgdown** using `usethis::use_pkgdown()`
      - Build website using `pkgdown::build_site()`
      - Push the contents of _root/docs_ folder to the remote repository
      - Activate Github Pages through repository settings and select _master/docs_ as website source. 
      - Website can be found [here](https://abhinabkadel.github.io/Nepalwildlife/)
      
#### Rerun `install()` to install the package with the necessary changes. 
#### **Note:** In between these steps, I performed `check()` statements to see if there were any errors. 


## Code of Conduct

Please note that the Nepalwildlife project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
