---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Nepalwildlife

<!-- badges: start -->
<!-- badges: end -->

Nepalwildlife package brings together a list of wild animals and plants found in Nepal. It contains of 1 tibble named `nepal_wildlife`.

## Installation

You can install the released version of Nepalwildlife from [Github](https://github.com/abhinabkadel/Nepalwildlife) with:

``` {r eval = FALSE}
install.packages("devtools")
devtools::install("abhinabkadel/Nepalwildlife")
```

## Example

How many species fall under different taxonomic groups in Nepal? Let's solve it using the dataset:

```{r example, message = FALSE}
library(Nepalwildlife) 
library(tidyverse)

nepal_wildlife %>% 
  count (`Taxonomic Group`)
```

## Code of Conduct

Please note that the Nepalwildlife project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
